---
title: "HIGH MOUNTAIN REGION IN Asia"
author: "Ridwan"
date: "2021 M02 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Data visualization: Altitudinal shift of climatically suitable area at risk of dengue transmission in the high mountain regions.
### Prepared: Ridwan Adeyemi Shittu
#### Master Thesis

```{r, echo=FALSE, include=TRUE}
rm(list = ls())  #### Remove all unwanted files in the environment
setwd("C:/thesisR/R_new")
library(raster)
library(rgdal)
library(rgeos)
library(geosphere)
library(ggpubr)
library(tidyverse)
library(dplyr)
library(ggforce) #for  sending difference face to new plot

```

### NB: Please run the first file analysis and graphs_ele before this files or Load the saved Rdata file for the script.
```{r, echo=FALSE}

# load("C:/thesisR/R_new/analysAndGraph_ele.RData") #load the previous file Analysis and graph ele

source("C:/thesisR/R_new/sort_def_function.R", echo=FALSE)
load("C:/thesisR/R_new/Cleaned_model_Ouputs_analysis.RData")

```

# Area analysis of suitable regions for Dengue transmission in South America HMR for current and future scenarios

## Area of Asia HMR
```{r }
#area for the shapefiles Asia(HMR)
asi_hmr_a <- areaPolygon(asi_hmr)

#print(asi_hmr_a/1000000)

#make a copy of crop binary raster
asihmr_bs_a <- asihmr_bs
# set the coordinate reference systemsystem
crs(asihmr_bs_a) <- proj.WGS84
#get sizes of all cells in raster [km2]
asihmr_bs_cellsize <- area(asihmr_bs_a, na.rm=TRUE, weights=FALSE)
# plot(asihmr_bs)
#delete NAs from vector of all raster cells ##NAs lie outside of the rastered region, can thus be omitted
asihmr_bs_cellsize <- asihmr_bs_cellsize[!is.na(asihmr_bs_cellsize)]

#compute area [km2] of all cells in asihmr_bs_area
asihmr_bs_area<-length(asihmr_bs_cellsize)*median(asihmr_bs_cellsize)
# Print area of the Asia(HMR) containing both the suitable and unsuitable regions to confirm the area of Asia(HMR) is correct

print(paste("Area of Asia(HMR) raster baseline:", round(asihmr_bs_area, digits = 1), "Km2"))


##plot the area computed
# graphics.off()
# x11(width = 8, height = 5)
# plot(asihmr_bs_a, main = "Area of Asia(HMR) Baseline Model") ### get a levelplot function
# plot(asi_hmr, add=TRUE)
```

## Current suitable area at risk of dengue
```{r}

asihmr_bs_suit_a <- asihmr_bs
crs(asihmr_bs_suit_a) <- proj.WGS84
asihmr_bs_suit_a[asihmr_bs_suit_a==0] <- NA # since our raster is categorical i.e 0 for unsuitable and 1 for suitable. Set the value of unsuitable to zero to get only the suitable areas out
# plot(asihmr_bs_suit_a)
# compute area [km2] of Asia(HMR)'s current suitable cells for dengue transmission
asihmr_bs_suit_cellsize <- area(asihmr_bs_suit_a, na.rm=TRUE, weights=FALSE)
asihmr_bs_suit_cellsize <- asihmr_bs_suit_cellsize[!is.na(asihmr_bs_suit_cellsize)]
asihmr_bs_suit_area<- length(asihmr_bs_suit_cellsize)*median(asihmr_bs_suit_cellsize)
# Print area of the Asia(HMR)'s current suitable region at right of dengue
print(paste("Area of Asia(HMR)'s current suitable regions for dengue tranmission:", round(asihmr_bs_suit_area, digits = 1), "Km2"))

asihmr_bs_unsuit_area <- asihmr_bs_area - asihmr_bs_suit_area
print(paste("Area of Asia(HMR)'s current unsuitable regions for dengue tranmission:", round(asihmr_bs_unsuit_area, digits = 1), "Km2"))
print(paste("percentage of Asia(HMR) Land current suitable for dengue transmission:", round((asihmr_bs_suit_area/asihmr_bs_area)*100,digits = 1), "%" ))



```
## Future scenario RCP 4.5 
### Year 2030 
```{r}
#year 2030 

asihmr_rcp4530_suit_a <- asihmr_rcp4530
crs(asihmr_rcp4530_suit_a) <- proj.WGS84
asihmr_rcp4530_suit_a[asihmr_rcp4530_suit_a==0] <- NA # raster is categorical i.e 0 for unsuitable and 1 for suitable. Set the value of unsuitable to zero to get only the suitable areas out
# plot(asihmr_rcp4530_suit_a)
# compute area [km2] of Asia(HMR)'s future scenario RCP4.5 year 2030 cells for dengue transmission
asihmr_rcp4530_suit_cellsize <- area(asihmr_rcp4530_suit_a, na.rm=TRUE, weights=FALSE)
asihmr_rcp4530_suit_cellsize <- asihmr_rcp4530_suit_cellsize[!is.na(asihmr_rcp4530_suit_cellsize)]
asihmr_rcp4530_suit_area<- length(asihmr_rcp4530_suit_cellsize)*median(asihmr_rcp4530_suit_cellsize)
# Print area of the Asia(HMR)'s future scenario RCP4.5 year 2030 region at right of dengue
print(paste("Area of Asia(HMR)'s future scenario RCP4.5 year 2030  suitable  for dengue tranmission:", round(asihmr_rcp4530_suit_area, digits = 1), "Km2"))

asihmr_rcp4530_unsuit_area <- asihmr_bs_area -asihmr_rcp4530_suit_area
print(paste("Area of Asia(HMR)'s future scenario RCP4.5 year 2030 unsuitable  for dengue tranmission:", round(asihmr_rcp4530_unsuit_area, digits = 1), "Km2"))

print(paste("Percentage of Asia(HMR) future scenario RCP4.5 year 2030 suitable for dengue transmission:", round((asihmr_rcp4530_suit_area/asihmr_bs_area)*100,digits = 1), "%" ))

```

### Year 2050
```{r}

# year 2050

asihmr_rcp4550_suit_a <- asihmr_rcp4550
crs(asihmr_rcp4550_suit_a) <- proj.WGS84
asihmr_rcp4550_suit_a[asihmr_rcp4550_suit_a==0] <- NA # raster is categorical i.e 0 for unsuitable and 1 for suitable. Set the value of unsuitable to zero to get only the suitable areas out
# plot(asihmr_rcp4550_suit_a)
# compute area [km2] of Asia(HMR)'s future scenario RCP4.5 year 2050 cells for dengue transmission
asihmr_rcp4550_suit_cellsize <- area(asihmr_rcp4550_suit_a, na.rm=TRUE, weights=FALSE)
asihmr_rcp4550_suit_cellsize <- asihmr_rcp4550_suit_cellsize[!is.na(asihmr_rcp4550_suit_cellsize)]
asihmr_rcp4550_suit_area<- length(asihmr_rcp4550_suit_cellsize)*median(asihmr_rcp4550_suit_cellsize)
# Print area of the Asia(HMR)'s future scenario RCP4.5 year 2050 region at right of dengue
print(paste("Area of Asia(HMR)'s future scenario RCP4.5 year 2050  suitable  for dengue tranmission:", round(asihmr_rcp4550_suit_area, digits = 1), "Km2"))

asihmr_rcp4550_unsuit_area <- asihmr_bs_area -asihmr_rcp4550_suit_area
print(paste("Area of Asia(HMR)'s future scenario RCP4.5 year 2050 unsuitable  for dengue tranmission:", round(asihmr_rcp4550_unsuit_area, digits = 1), "Km2"))

print(paste("Percentage of Asia(HMR) future scenario RCP4.5 year 2050 suitable for dengue transmission:", round((asihmr_rcp4550_suit_area/asihmr_bs_area)*100,digits = 1), "%" ))

```


### Year 2070
```{r}
# year 2070
asihmr_rcp4570_suit_a <- asihmr_rcp4570
crs(asihmr_rcp4570_suit_a) <- proj.WGS84
asihmr_rcp4570_suit_a[asihmr_rcp4570_suit_a==0] <- NA # raster is categorical i.e 0 for unsuitable and 1 for suitable. Set the value of unsuitable to zero to get only the suitable areas out
# plot(asihmr_rcp4570_suit_a)
# compute area [km2] of Asia(HMR)'s future scenario RCP4.5 year 2070 cells for dengue transmission
asihmr_rcp4570_suit_cellsize <- area(asihmr_rcp4570_suit_a, na.rm=TRUE, weights=FALSE)
asihmr_rcp4570_suit_cellsize <- asihmr_rcp4570_suit_cellsize[!is.na(asihmr_rcp4570_suit_cellsize)]
asihmr_rcp4570_suit_area<- length(asihmr_rcp4570_suit_cellsize)*median(asihmr_rcp4570_suit_cellsize)
# Print area of the Asia(HMR)'s future scenario RCP4.5 year 2070 region at right of dengue
print(paste("Area of Asia(HMR)'s future scenario RCP4.5 year 2070  suitable  for dengue tranmission:", round(asihmr_rcp4570_suit_area, digits = 1), "Km2"))

asihmr_rcp4570_unsuit_area <- asihmr_bs_area -asihmr_rcp4570_suit_area
print(paste("Area of Asia(HMR)'s future scenario RCP4.5 year 2070 unsuitable  for dengue tranmission:", round(asihmr_rcp4570_unsuit_area, digits = 1), "Km2"))

print(paste("Percentage of Asia(HMR) future scenario RCP4.5 year 2070 suitable for dengue transmission:", round((asihmr_rcp4570_suit_area/asihmr_bs_area)*100,digits = 1), "%" ))
```
## Future scenario RCP 8.5 
### Year 2030 
```{r}
#year 2030 
asihmr_rcp8530_suit_a <- asihmr_rcp8530
crs(asihmr_rcp8530_suit_a) <- proj.WGS84
asihmr_rcp8530_suit_a[asihmr_rcp8530_suit_a==0] <- NA # raster is categorical i.e 0 for unsuitable and 1 for suitable. Set the value of unsuitable to zero to get only the suitable areas out
# plot(asihmr_rcp8530_suit_a)

asihmr_rcp8530_suit_cellsize <- area(asihmr_rcp8530_suit_a, na.rm=TRUE, weights=FALSE)
asihmr_rcp8530_suit_cellsize <- asihmr_rcp8530_suit_cellsize[!is.na(asihmr_rcp8530_suit_cellsize)]
asihmr_rcp8530_suit_area<- length(asihmr_rcp8530_suit_cellsize)*median(asihmr_rcp8530_suit_cellsize)
# Print area of the Asia(HMR)'s future scenario RCP8.5 year 2030 region at right of dengue
print(paste("Area of Asia(HMR)'s future scenario RCP8.5 year 2030  suitable  for dengue tranmission:", round(asihmr_rcp8530_suit_area, digits = 1), "Km2"))

asihmr_rcp8530_unsuit_area <- asihmr_bs_area -asihmr_rcp8530_suit_area
print(paste("Area of Asia(HMR)'s future scenario RCP8.5 year 2030 unsuitable  for dengue tranmission:", round(asihmr_rcp8530_unsuit_area, digits = 1), "Km2"))

print(paste("Percentage of Asia(HMR) future scenario RCP8.5 year 2030 suitable for dengue transmission:", round((asihmr_rcp8530_suit_area/asihmr_bs_area)*100,digits = 1), "%" ))


```

### Year 2050
```{r}

# year 2050
asihmr_rcp8550_suit_a <- asihmr_rcp8550
crs(asihmr_rcp8550_suit_a) <- proj.WGS84
asihmr_rcp8550_suit_a[asihmr_rcp8550_suit_a==0] <- NA # raster is categorical i.e 0 for unsuitable and 1 for suitable. Set the value of unsuitable to zero to get only the suitable areas out
# plot(asihmr_rcp8550_suit_a)
# compute area [km2] of Asia(HMR)'s future scenario RCP8.5 year 2050  cells for dengue transmission
asihmr_rcp8550_suit_cellsize <- area(asihmr_rcp8550_suit_a, na.rm=TRUE, weights=FALSE)
asihmr_rcp8550_suit_cellsize <- asihmr_rcp8550_suit_cellsize[!is.na(asihmr_rcp8550_suit_cellsize)]
asihmr_rcp8550_suit_area<- length(asihmr_rcp8550_suit_cellsize)*median(asihmr_rcp8550_suit_cellsize)
# Print area of the Asia(HMR)'s future scenario RCP8.5 year 2050  region at right of dengue
print(paste("Area of Asia(HMR)'s future scenario RCP8.5 year 2050  suitable  for dengue tranmission:", round(asihmr_rcp8550_suit_area, digits = 1), "Km2"))

asihmr_rcp8550_unsuit_area <- asihmr_bs_area -asihmr_rcp8550_suit_area
print(paste("Area of Asia(HMR)'s future scenario RCP8.5 year 2050 unsuitable  for dengue tranmission:", round(asihmr_rcp8550_unsuit_area, digits = 1), "Km2"))

print(paste("Percentage of Asia(HMR) future scenario RCP8.5 year 2050 suitable for dengue transmission:", round((asihmr_rcp8550_suit_area/asihmr_bs_area)*100,digits = 1), "%" ))


```


### Year 2070
```{r}
# year 2070
asihmr_rcp8570_suit_a <- asihmr_rcp8570
crs(asihmr_rcp8570_suit_a) <- proj.WGS84
asihmr_rcp8570_suit_a[asihmr_rcp8570_suit_a==0] <- NA # raster is categorical i.e 0 for unsuitable and 1 for suitable. Set the value of unsuitable to zero to get only the suitable areas out
# plot(asihmr_rcp8570_suit_a)
# compute area [km2] of Asia(HMR)'s future scenario RCP8.5 year 2070 cells for dengue transmission
asihmr_rcp8570_suit_cellsize <- area(asihmr_rcp8570_suit_a, na.rm=TRUE, weights=FALSE)
asihmr_rcp8570_suit_cellsize <- asihmr_rcp8570_suit_cellsize[!is.na(asihmr_rcp8570_suit_cellsize)]
asihmr_rcp8570_suit_area<- length(asihmr_rcp8570_suit_cellsize)*median(asihmr_rcp8570_suit_cellsize)
# Print area of the Asia(HMR)'s future scenario RCP8.5 year 2070 region at right of dengue
print(paste("Area of Asia(HMR)'s future scenario RCP8.5 year 2070  suitable  for dengue tranmission:", round(asihmr_rcp8570_suit_area, digits = 1), "Km2"))

asihmr_rcp8570_unsuit_area <- asihmr_bs_area -asihmr_rcp8570_suit_area
print(paste("Area of Asia(HMR)'s future scenario RCP8.5 year 2070 unsuitable  for dengue tranmission:", round(asihmr_rcp8570_unsuit_area, digits = 1), "Km2"))

print(paste("Percentage of Asia(HMR) future scenario RCP8.5 year 2070 suitable for dengue transmission:", round((asihmr_rcp8570_suit_area/asihmr_bs_area)*100,digits = 1), "%" ))

```


# Elevation gradient analysis of Area of HMR suitable for dengue transmission.



### Current
```{r}
## baseline
asihmr_bs_suit_sps <- asihmr_bs_suit
asihmr_bs_suit_sps
asihmr_bs_suit_sps_xy <- as.data.frame(asihmr_bs_suit_sps, xy = T) %>% drop_na() #conver the raster to dataframe and remove NAs 

# View(asihmr_bs_suit_sps_xy)
asihmr_bs_suit_pt <- SpatialPoints(asihmr_bs_suit_sps_xy[1:2], proj4string = crs(asihmr_bs_suit_sps))
#plot(asihmr_bs_suit_pt)
asihmr_bs_suit_sps_elv <- raster::extract(eleva, asihmr_bs_suit_pt)
#View(asihmr_bs_suit_sps_elv)
hist(asihmr_bs_suit_sps_elv)
asihmr_bs_suit_sps_elv <- round(asihmr_bs_suit_sps_elv)
asihmr_bs_suit_sps_elv_df <- table(asihmr_bs_suit_sps_elv)
asihmr_bs_suit_sps_elv_df<- as.data.frame(asihmr_bs_suit_sps_elv_df)
```

## Future scenario RCP 4.5 

### Year 2030
```{r}
asihmr_rcp4530_suit_sps <- asihmr_rcp4530_suit
# plot(asihmr_rcp4530_suit)
asihmr_rcp4530_suit_sps
asihmr_rcp4530_suit_sps_xy <- as.data.frame(asihmr_rcp4530_suit_sps, xy = T) %>% drop_na()
# asihmr_rcp4530_suit_sps_xy<- na.omit(asihmr_rcp4530_suit_sps_xy)
#View(asihmr_rcp4530_suit_sps_xy)
asihmr_rcp4530_suit_pt <- SpatialPoints(asihmr_rcp4530_suit_sps_xy[1:2], proj4string = crs(asihmr_rcp4530_suit_sps))
# plot(asihmr_rcp4530_suit_pt)
asihmr_rcp4530_suit_sps_elv <- raster::extract(eleva, asihmr_rcp4530_suit_pt)
#View(asihmr_rcp4530_suit_sps_elv)
asihmr_rcp4530_suit_sps_elv <- round(asihmr_rcp4530_suit_sps_elv)
asihmr_rcp4530_suit_sps_elv_df <- table(asihmr_rcp4530_suit_sps_elv) %>%  as.data.frame()
# asihmr_rcp4530_suit_sps_elv_df<- as.data.frame(asihmr_rcp4530_suit_sps_elv_df)
#View(asihmr_rcp4530_suit_sps_elv_df)


```

### Year 2050
```{r}
asihmr_rcp4550_suit_sps <- asihmr_rcp4550_suit
# plot(asihmr_rcp4550_suit)
asihmr_rcp4550_suit_sps
asihmr_rcp4550_suit_sps_xy <- as.data.frame(asihmr_rcp4550_suit_sps, xy = T) %>% drop_na()
# asihmr_rcp4550_suit_sps_xy<- na.omit(asihmr_rcp4550_suit_sps_xy)
#View(asihmr_rcp4550_suit_sps_xy)
asihmr_rcp4550_suit_pt <- SpatialPoints(asihmr_rcp4550_suit_sps_xy[1:2], proj4string = crs(asihmr_rcp4550_suit_sps))
# plot(asihmr_rcp4550_suit_pt)
asihmr_rcp4550_suit_sps_elv <- raster::extract(eleva, asihmr_rcp4550_suit_pt)
#View(asihmr_rcp4550_suit_sps_elv)
hist(asihmr_rcp4550_suit_sps_elv )
asihmr_rcp4550_suit_sps_elv <- round(asihmr_rcp4550_suit_sps_elv)
asihmr_rcp4550_suit_sps_elv_df <- table(asihmr_rcp4550_suit_sps_elv) %>% as.data.frame()
# asihmr_rcp4550_suit_sps_elv_df<- as.data.frame(asihmr_rcp4550_suit_sps_elv_df)

```

### Year 2070

```{r}
asihmr_rcp4570_suit_sps <- asihmr_rcp4570_suit
# plot(asihmr_rcp4570_suit)
asihmr_rcp4570_suit_sps
asihmr_rcp4570_suit_sps_xy <- as.data.frame(asihmr_rcp4570_suit_sps, xy = T) %>% drop_na()
# asihmr_rcp4570_suit_sps_xy<- na.omit(asihmr_rcp4570_suit_sps_xy)
#View(asihmr_rcp4570_suit_sps_xy)
asihmr_rcp4570_suit_pt <- SpatialPoints(asihmr_rcp4570_suit_sps_xy[1:2], proj4string = crs(asihmr_rcp4570_suit_sps))
# plot(asihmr_rcp4570_suit_pt)
asihmr_rcp4570_suit_sps_elv <- raster::extract(eleva, asihmr_rcp4570_suit_pt)
hist(asihmr_rcp4570_suit_sps_elv)
#View(asihmr_rcp4570_suit_sps_elv)
asihmr_rcp4570_suit_sps_elv <- round(asihmr_rcp4570_suit_sps_elv)
asihmr_rcp4570_suit_sps_elv_df <- table(asihmr_rcp4570_suit_sps_elv) %>% as.data.frame()
# asihmr_rcp4570_suit_sps_elv_df<- as.data.frame(asihmr_rcp4570_suit_sps_elv_df)

```

## Future scenario RCP 8.5 

### Year 2030
```{r}
asihmr_rcp8530_suit_sps <- asihmr_rcp8530_suit
# plot(asihmr_rcp8530_suit)
asihmr_rcp8530_suit_sps
asihmr_rcp8530_suit_sps_xy <- as.data.frame(asihmr_rcp8530_suit_sps, xy = T) %>% drop_na()
# asihmr_rcp8530_suit_sps_xy<- na.omit(asihmr_rcp8530_suit_sps_xy)
#View(asihmr_rcp8530_suit_sps_xy)
asihmr_rcp8530_suit_pt <- SpatialPoints(asihmr_rcp8530_suit_sps_xy[1:2], proj4string = crs(asihmr_rcp8530_suit_sps))
# plot(asihmr_rcp8530_suit_pt)
asihmr_rcp8530_suit_sps_elv <- raster::extract(eleva, asihmr_rcp8530_suit_pt)
#View(asihmr_rcp8530_suit_sps_elv)
asihmr_rcp8530_suit_sps_elv <- round(asihmr_rcp8530_suit_sps_elv)
asihmr_rcp8530_suit_sps_elv_df <- table(asihmr_rcp8530_suit_sps_elv) %>% as.data.frame()
# asihmr_rcp8530_suit_sps_elv_df<- as.data.frame(asihmr_rcp8530_suit_sps_elv_df)
# View(asihmr_rcp8530_suit_sps_elv_df)
```

## Year 2050
```{r}
asihmr_rcp8550_suit_sps <- asihmr_rcp8550_suit
# plot(asihmr_rcp8550_suit)
asihmr_rcp8550_suit_sps
asihmr_rcp8550_suit_sps_xy <- as.data.frame(asihmr_rcp8550_suit_sps, xy = T) %>% drop_na()
# asihmr_rcp8550_suit_sps_xy<- na.omit(asihmr_rcp8550_suit_sps_xy)
#View(asihmr_rcp8550_suit_sps_xy)
asihmr_rcp8550_suit_pt <- SpatialPoints(asihmr_rcp8550_suit_sps_xy[1:2], proj4string = crs(asihmr_rcp8550_suit_sps))
# plot(asihmr_rcp8550_suit_pt)
asihmr_rcp8550_suit_sps_elv <- raster::extract(eleva, asihmr_rcp8550_suit_pt)
#View(asihmr_rcp8550_suit_sps_elv)
hist(asihmr_rcp8550_suit_sps_elv)
asihmr_rcp8550_suit_sps_elv <- round(asihmr_rcp8550_suit_sps_elv)
asihmr_rcp8550_suit_sps_elv_df <- table(asihmr_rcp8550_suit_sps_elv) %>% as.data.frame()
# asihmr_rcp8550_suit_sps_elv_df<- as.data.frame(asihmr_rcp8550_suit_sps_elv_df)
# View(asihmr_rcp8550_suit_sps_elv_df)

```
## Year 2070
```{r}
###asihmr_rcp8570_suit
asihmr_rcp8570_suit_sps <- asihmr_rcp8570_suit
# plot(asihmr_rcp8570_suit)
asihmr_rcp8570_suit_sps
asihmr_rcp8570_suit_sps_xy <- as.data.frame(asihmr_rcp8570_suit_sps, xy = T) %>% drop_na()
# asihmr_rcp8570_suit_sps_xy<- na.omit(asihmr_rcp8570_suit_sps_xy)
#View(asihmr_rcp8570_suit_sps_xy)
asihmr_rcp8570_suit_pt <- SpatialPoints(asihmr_rcp8570_suit_sps_xy[1:2], proj4string = crs(asihmr_rcp8570_suit_sps))
# plot(asihmr_rcp8570_suit_pt)
asihmr_rcp8570_suit_sps_elv <- raster::extract(eleva, asihmr_rcp8570_suit_pt)
#View(asihmr_rcp8570_suit_sps_elv)
hist(asihmr_rcp8570_suit_sps_elv)
asihmr_rcp8570_suit_sps_elv <- round(asihmr_rcp8570_suit_sps_elv)
asihmr_rcp8570_suit_sps_elv_df <- table(asihmr_rcp8570_suit_sps_elv) %>% as.data.frame()


```

## Summary Statistic for the elevation gradient of Asia HMR
### New Container dataframe for scenarios
```{r}
asihmr_baseline_df1 <-   data.frame(Scenarios = "Baseline", elevation = asihmr_bs_suit_sps_elv_df$asihmr_bs_suit_sps_elv, Pixels= asihmr_bs_suit_sps_elv_df$Freq)
asihmr_rcp45_2030_df1 <- data.frame(Scenarios = "RCP4.5 2030", elevation = asihmr_rcp4530_suit_sps_elv_df$asihmr_rcp4530_suit_sps_elv, Pixels = asihmr_rcp4530_suit_sps_elv_df$Freq)

asihmr_rcp45_2050_df1 <- data.frame(Scenarios = "RCP4.5 2050", elevation = asihmr_rcp4550_suit_sps_elv_df$asihmr_rcp4550_suit_sps_elv, Pixels=asihmr_rcp4550_suit_sps_elv_df$Freq)

asihmr_rcp45_2070_df1 <- data.frame(Scenarios = "RCP4.5 2070", elevation = asihmr_rcp4570_suit_sps_elv_df$asihmr_rcp4570_suit_sps_elv, Pixels=asihmr_rcp4570_suit_sps_elv_df$Freq)
asihmr_rcp85_2030_df1 <- data.frame(Scenarios = "RCP8.5 2030", elevation = asihmr_rcp8530_suit_sps_elv_df$asihmr_rcp8530_suit_sps_elv, Pixels=asihmr_rcp8530_suit_sps_elv_df$Freq)

asihmr_rcp85_2050_df1 <- data.frame(Scenarios = "RCP8.5 2050", elevation = asihmr_rcp8550_suit_sps_elv_df$asihmr_rcp8550_suit_sps_elv, Pixels=asihmr_rcp8550_suit_sps_elv_df$Freq)

asihmr_rcp85_2070_df1 <- data.frame(Scenarios = "RCP8.5 2070", elevation = asihmr_rcp8570_suit_sps_elv_df$asihmr_rcp8570_suit_sps_elv, Pixels= asihmr_rcp8570_suit_sps_elv_df$Freq)

asihmr_dengue_rbind <- rbind(asihmr_baseline_df1, asihmr_rcp45_2030_df1, asihmr_rcp45_2050_df1,asihmr_rcp45_2070_df1, asihmr_rcp85_2030_df1, asihmr_rcp85_2050_df1, asihmr_rcp85_2070_df1 ) 
head(asihmr_dengue_rbind)
str(asihmr_dengue_rbind) # note the elevation values are stored as factor. This is an error, therefore, we conver the factors to numeric

#conver elevation in factor to character to numeric
asihmr_dengue_rbind$elevation <- as.numeric(as.character(asihmr_dengue_rbind$elevation))

#Summary statistics
asihmr_ele_summary <- do.call(cbind, tapply(asihmr_dengue_rbind$elevation, asihmr_dengue_rbind$Scenarios, summary)) # using do call one can combine list of the summary to columns combine
asihmr_ele_summary_t <- as.data.frame(t(as.matrix(asihmr_ele_summary))) #make a transpose: change the columns to row and rows to columns
asihmr_ele_summary_t
asihmr_ele_summary
getwd()
write.csv(asihmr_ele_summary_t, "C:/thesisR/R_new/HMRs/Asia_HMR/asiHMR_elevation_summary.csv")
```
### Sorting the elevation values of suitable areas into different frequency.

```{r}
asihmr_dengue_rbind2 <- asihmr_dengue_rbind
asihmr_dengue_rbind2 <- sort_def2(asihmr_dengue_rbind2)
tail(asihmr_dengue_rbind2,100)
head(asihmr_dengue_rbind2)

asihmr_dengue_rbind2$sorting <-factor(asihmr_dengue_rbind2$sorting, levels = c("<0","0-199","200-399", "400 -599", "600-799","800-999", "1000-1199", "1200-1399","1400-1599", "1600-1799","1800-1999","2000-2199","2200-2399", "2400-2599", "2600-2799",  "2800-2999", "3000-3199", "3200-3399", "3400-3599","3600-3799","3800-3999","4000 - 4199 ","4200-4399", "> 4400"))

```

### Generating the scenario plots for number of pixel in each elevation gradient.
```{r}
# to know the number of pages require
ggplot(data = asihmr_dengue_rbind2, aes(x=sorting, y = Pixels))+
  geom_bar(stat = 'identity', fill = "#fdb924", position = position_dodge(preserve = "total"))+ 
  facet_wrap_paginate(~Scenarios, scales="free_y", nrow = 1, ncol = 1)+
  scale_y_continuous(breaks = pretty(asihmr_dengue_rbind$Pixels, n=10))+
  labs(x="Elevation range [m ]", y = 'No. of Pixels',
       title = "Altitudinal distribution of areas suitable for dengue transmission",
       subtitle = "Asia(HMR) ")+
  theme(strip.text=element_text(size = 30)) -> p.elegrt

no_p.elegrt <- n_pages(p.elegrt)
no_p.elegrt 
#save each barplot to as individual page  to a pdf
getwd()
pdf("C:/thesisR/R_new/HMRs/Asia_HMR/AsiHMR_pAll.pdf") 
# loop over the facet plots
for(i in 1:no_p.elegrt){
  ggplot(data = asihmr_dengue_rbind2, aes(x=sorting, y = Pixels))+
    geom_bar(stat = 'identity', fill = "#fdb924", position = position_dodge(preserve = "total"), width = .2)+ 
    facet_wrap_paginate(~Scenarios, scales="free_y", nrow = 1, ncol = 1, page = i)+
    scale_y_continuous(breaks = pretty(asihmr_dengue_rbind$Pixels, n=10))+
    labs(x="Elevation range [m ]", y = 'No. of Pixels',
         title = "Altitudinal distribution of areas suitable for dengue transmission",
         subtitle = "Asia(HMR) ")+
    theme_minimal()+
    theme(strip.text=element_text(size = 30), axis.text.x = element_text(angle = 45)) -> p.elegrt
  print(p.elegrt)
}
dev.off()

```


